Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-29 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

For resolving tiny structures like single cytoskeleton fibers, nanoparticle, with sizes smaller
than the diffraction-limit, or protein complexes, it would be helpful to use microscopy
techniques, which can resolve structures beyond the diffraction limit.

One of that techniques is STED microscopy (see section~\ref{sec:deterministic-approaches}). In a 
proof-of-principle study the topography of a group of fixed HeLa cells together with the 
distribution of actin filaments was investigated \cite{Hagemann2018}. Although both methods were 
able to investigate living cells, the cells needs to be fixed in that study, because the 
investigation was consecutively done onto two microscopes. The topography was measured with SICM 
and the distribution of actin with STED microscopy (see figure~\ref{fig:SICM_STED1}).

@@

>>>>

For resolving tiny structures like single cytoskeleton fibers, nanoparticle, with sizes smaller
than the diffraction-limit, or protein complexes, it would be helpful to use microscopy
techniques, which can resolve structures beyond the diffraction limit of light (see 
equation~\ref{eq:diffraction-limit}; \cite{Abbe1873}).

% Hier vielleicht auch noch Fig. 3 aus der ACSNano-Publikation einfügen??? Würde vielleicht ganz
% gut passen!?

One of that techniques, that can resolve structures beyond the diffraction limit, is STED 
microscopy (see section~\ref{sec:deterministic-approaches}). In a proof-of-principle study the 
topography of a group of fixed HeLa cells together with the distribution of actin filaments was
investigated \cite{Hagemann2018}. Although both methods were able to investigate living cells, the 
cells were fixed in that study, because the investigation was done consecutively onto two 
microscopes. The topography was measured with SICM and the distribution of actin with STED 
microscopy (see figure~\ref{fig:SICM_STED1}).

@@

The topography of a group of more than four fixed HeLa cells can be seen in 
figure~\ref{fig:SICM_STED1}Aa the corresponding slope representation in Ab, the confocal image in 
Ac and the STED image in Ad. The confocal and STED image represents the same region as marked with 
a black dotted line in Aa and Ab. Many different cell topographies were visible in Aa.

A round cell with a maximum height of approximately 16.4~{\textmu}m height can be seen in the 
right upper region of the image (marked with a purple arrow in Aa/Ab/Ac/Ad). The cell next to this 
was flat and extending (?) the scanned region (yellow arrow). A second flat but smaller cell was 
marked with a with arrow ending with a white dot. Marked with a purple arrow ending with a purple
dot was a small and a kind of roundish cells. This cell besitzt (german)
a protrusion (white arrowhead), those magnification could be seen in Dd/Df respectively in De/Dg. 
The protrusion was approximately 4~{\textmu}m long and 5~{\textmu}m high (Dc, 
\cite{Hagemann2018}).

Beside the different topographies of these two cells, they also display different types of actin 
fibres. In the inside of the first mentioned round cell nearly no actin signal could be detected 
(some dot-like structures were marked with purple arrowheads), whereas at the borders of the cell 
some hair-like structures were visible (white arrow). The long, flat cell showed some long actin 
fibres (yellow arrowheads).
